Title

### 2024-06-08 paper/main.tex
udpates

\emph{Causal discovery} is the process of identifying and understanding causal
relationships among variables in a dataset. Causal discovery techniques are
used typically to understand and estimate causal effects between variables. In
the To perform any causal effect estimation using Directed Acyclic Graphs
(DAGs) or Structural Equation Models (SEMs), researchers need to first
construct a causal structure. In the field of DAGs, a lot of attention has been
put on developing automated algorithms that can construct these DAGs from data.
These algorithm takes different approaches to causal discovery such as
constraint-based algorithms such as PC and Fast Causal Infenrece (FCI) where
the algorithm tries to match the conditional independences in the data to the
ones impled by the model, score-based methods such as Hill-Climb Search, Greedy
Equivalence Search (GES)  where the algorithm tries to find a model that has
the best score given some scoring metric, and continuous optimization where the
problem is formulated as a constrained optimization problem such as No Tears, and
some hybrid approaches.

@@

On the other hand, in the field of Structural Equation Models (SEMs), models
are also typically constructed by hand. And a lot of focus has been put on
developing tools to help researchers in constructing these models. Researchers
typically come up with an initial model, which then they use the data and
expert knowledge to make modifications to. This process is commonly known as
\emph{Specification Search}. These tools can then be used to guide the
researchers in suggesting best ways to modify the model. For example,
\emph{modification indices} take the initial drawn model, and make all possible
modifications to the model to check which modification improves the model fit
the best. Based on this information, the researcher can make modifications to
the model and reiterate this process till they get something that they are
satisfied with.

@@

\subsection{Association Measures}
In this section, we give a background on some of the commonly used effect size
measures in the context of CI testing.

@@

\section{Effect size for mixed data}
In this section, we use canonical correlations to define an effect size measure
for mixed data CI tests. Our approach is similar to the approach used for the
continuous variable case.

>>>>

\emph{Causal discovery} is the process of identifying and understanding causal
relationships among variables in a dataset.  To perform any causal effect
estimation using Directed Acyclic Graphs (DAGs) or Structural Equation Models
(SEMs), researchers need to first construct a causal structure. In the field of
DAGs, a lot of attention has been put on developing automated algorithms that
can construct these DAGs from data. These algorithm takes different approaches
to causal discovery such as constraint-based algorithms such as PC and Fast
Causal Infenrece (FCI) where the algorithm tries to match the conditional
independences in the data to the ones impled by the model, score-based methods
such as Hill-Climb Search, Greedy Equivalence Search (GES)  where the algorithm
tries to find a model that has the best score given some scoring metric, and
continuous optimization where the problem is formulated as a constrained
optimization problem such as No Tears, and some hybrid approaches.

@@

On the other hand, in the field of Structural Equation Models (SEMs), models
are also typically constructed by hand. And a lot of focus has been put on
developing tools to help researchers in constructing these models. Researchers
typically come up with an initial model, which then they use the data and
expert knowledge to make modifications to. This process is commonly known as
\emph{Specification Search}. These tools can then be used to guide the
researchers in suggesting best ways to modify the model combined with the
expert knowledge. For example, \emph{modification indices} take the initial
drawn model, and make all possible modifications to the model to check which
modification improves the model fit the best. Based on this information, the
researcher can make modifications to the model and reiterate this process till
they get something that they are satisfied with.

@@

\subsection{Measures of Association}
In this section, we give a background on some of the commonly used effect size
measures in the context of CI testing.

@@

\section{Measure of Association for mixed data}
In this section, we use canonical correlations to define an effect size measure
for mixed data CI tests. Our approach is similar to the approach used for the
continuous variable case.
